\section{Conclusion}
I learned a lot by doing this project . During this period I got to learn a vast 
number of technologies. These are lsited below :
\begin{itemize}
\item {\bf{Operating system}}: Ubuntu
\item {\bf{Languages used}}: PHP, Html, CSS, JQuery
\item {\bf{Database}}: MySql
\item {\bf{Typesetting}}: LaTex
\item {\bf{Documenter}}: Doxygen
\end{itemize}
So during this project I learned all the above things. Above all I got to know 
how Softwares are developed from the scratch. Planning, designing, developing code, 
working in a team, testing etc. These are all very precious things I got to learn 
during this period. If I talk about the project, Elearning project reduce a lot of 
manual work. It has automated most of the class work. It is a great project with wider scope and it can be implemented on every school or college as it is user friendly and less time consuming.
\section{Current status}
Elearning System is currently running on my local machine. It has 
automated most of the class work of an institute.
Software has following applications in it:
\begin{itemize}
\item Login and registration
\item Add new Student/Teacher.
\item Upload Assignments.
\item View Grades.
\item Check Progress.
\item Add Announcements/Events
\item Send Messages
\end{itemize}
 
\section{Future Scope}
Elearning System reduces the manual work and save the time. It also reduces 
the man power and reduces the burden of handling lots of data. It keeps the backup 
of the record stored. As the project is complete but still there are many more 
things or areas which can be added to the project to make that more reliable. 
It has already done following things:
\begin{itemize}
\item The project has already improved the learning experience to a huge extent
by automating the processes, reducing the time tremendously from several days to a
few minutes and cutting costs hugely.
\item Although automated to a large extent, Elearning is still in its initial development stages and there is still scope for a lot of development.
\item It is developed using the open source technologies, so it's code will always be available and every institute can upgrade it for using it on their own institute server.
\item It can be deployed on the college server keeping in mind it's benefits, as it will take the class experience to whole new extent.
\item We plan to add a lot of other features some of which are availability of the sessional exam scores and also the answer sheets of all examinations held during the current semester.
\end{itemize}

\noindent With the advancement in technology everyday i think that this project has a huge scope for future use. We know that there are many popular Online learning systems for example Moodle is one of them. It has connected a large number of people around the world that shows that people are ready to move from pen paper to computer for learning. So keeping in mind these things Elearning System has a great scope for future. I hope it will be deployed on our college server soon.
