A freight company is that which specializes in the moving (or \lq forwarding\rq)
of freight, or cargo, from one place to another. There are thousands 
of freight companies in business worldwide, many of which are members 
of certain organizations. Open Freight Carriers is a company dedicated 
to offer a wide array of freight and logistics services ranging from 
local handling and shipping to global supply chain management and 
strives to be the preferred trade expert and logistics provider for 
shippers needing innovative, cost-effective and integrated supply chain 
solutions to move their products from the point of production to the 
point of consumption. Today, they provide the technology, expertise 
and solutions supported by a network with the aim of simplifying 
national trade for their customers.

Their solutions aim to grant you the benefit of flexible market entry 
and exit, key to meeting the challenges of today's competitive global 
environment. Their team works closely with the customers to understand 
their business, their needs, goals and strategies and is committed to 
deliver exceptional, personalized and flexible services for all 
transportation and logistics needs.

Open Freight Carriers is also a renowned specialist in the field of 
handling complete industrial projects including transportation and 
lifting of ultra heavy or ultra large cargo. Moreover, they offer the 
customers full consultation support regarding trade agreements, duties, 
taxes and licenses in connection to international transportation.


